### 2025-07-17 manuscript/part2.tex
test description

\section{Testing}
\section{Parsing Speed}

>>>>

\section{Testing}

The Langium project's test suite is initialized via Vitest in the scaffolding-generated environment and is organized into three distinct categories: parsing, linking,
and validation. Parsing tests verify that all grammar rules and their associated assignments are correctly recognized and transformed into the appropriate CST and AST
node types. Linking tests focus on scope management and reference resolution, ensuring that identifiers and imports are resolved accurately; notably,
import resolution tests employ a virtual file system to simulate file paths and confirm that cross-file references function as intended. Validation tests then examine
semantic constraints and type correctness, asserting that the constructed AST adheres to the language's typing and business-logic rules. Across all categories,
the tests interact directly with CST and AST nodes, making precise assertions that guarantee the language implementation remains consistent and reliable.

\section{Parsing Speed}
